Treatment heterogeneity in comparative effectiveness of teriparatide vs bisphosphonates: multi-database cohort study

### 2021-12-03 submission/manuscript.rmd
fix figure labels and themes; switch to cowplot

\newpage
```{r plotMeta, echo=FALSE, fig.cap="Calibrated hazard ratios for the 3 outcomes of interest across the 3 considered databases using a set of 126 negative controls. Values below 1 favour teriparatide, while values above 1 favour bisphosphonates.", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here::here("figures/plotMeta.tiff")))
```

>>>>

\newpage
```{r overallCovariateBalance, cache = TRUE, echo = FALSE, warning=FALSE, fig.cap="Calibrated overall results"}
grid::grid.raster(tiff::readTIFF(here("figures/OverallCovariateBalance.tiff")))
```

\newpage
```{r overallPsDensity, cache = FALSE, echo = FALSE, warning=FALSE, fig.cap="Calibrated overall results"}
grid::grid.raster(tiff::readTIFF(here("figures/OverallPsDensity.tiff")))
```

\newpage
```{r overallNcPlot, cache = FALSE, echo = FALSE, warning=FALSE, fig.cap="Overall negative control plot."}
grid::grid.raster(tiff::readTIFF(here("figures/OverallNcPlot.tiff")))
```

\newpage
```{r plotMeta, echo=FALSE, warning=FALSE, fig.cap="Calibrated hazard ratios for the 3 outcomes of interest across the 3 considered databases using a set of 126 negative controls. Values below 1 favour teriparatide, while values above 1 favour bisphosphonates.", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here::here("figures/plotMeta.tiff")))
```
